\documentclass{article}
\usepackage{cv}

\title{Curriculum Vitae}
\author{Benjamin A Shaw}

\begin{document}

% CV Header section
{\huge{\color{slateblue}\textbf{Benjamin Shaw}}}\\
\rule{\textwidth}{0.5mm}\\

\begin{personaldetails}
{21$^{st}$ October 1984}
{https://github.com/benshaw}
{+1 250 200 0393}
{benjamin.alexander.shaw@gmail.com}
\end{personaldetails}

% Personal profile section

\section*{Personal Profile}
\begin{itemize}
  \item Technical leader with a track record of successful delivery and a broad skill set acquired from a diverse background. I enjoy working with people and technology to solve complex problems. Specialised in applying software best practices to scale Machine Learning.
\end{itemize}

\section*{Summary}
\begin{itemize}
  \item 17 years Professional Software Engineer.
  \item Leadership and team building.
  \item MLOps/ML Engineering.
  \item Backend development.
  \item DevOps/Infrastructure.
\end{itemize}

% Employment History section
\section*{Employment History}


\begin{job}
{Mar 2022-}{Present}
{Scribd, Remote Canada}
{https://www.scribd.com/home}
{Senior Manager Machine Learning Platform}%
{Product owner, technical lead and manager for a team that designed, built and maintained the platform that enabled Machine Learning at scale and drove the Scribd user experience. The ML Platform provided a curated developer experience for ML developers throughout the entire ML Life cycle, a self service platform that supported developers from initial model experimentation, through testing, deployment and monitoring. The goal of the platform was to increase velocity of ML developers and control technical debt allowing the ML org to scale. The platform support a large number of models in production with use cases from spam detection, to recommendations and LLM's. Amongst other things the platform contained a feature store, experimentation tracker, model db, Embedding based retrieval, model deployment pipelines, real time endpoints and batch inference solutions \\
\rule{0mm}{5mm}\textbf{Experience:} Project Management, Product Manager, Developing road maps, Team building, Team culture, Feature Store, Recommendations, LLM, Real-time Model Inference, Batch Model Inference, AWS, Embedding based retrieval }
\end{job}


\begin{job}
{Apr 2021-}{Jan 2022}
{Scribd, Remote Canada}
{https://www.scribd.com/home}
{Staff Engineer Machine Learning Platform}%
{Responsible for designing and implementing a self service platform for version controlling Machine Learning models as well as the Continuous Integration and Delivery process for delivering these models to production at scale \\
\rule{0mm}{5mm}\textbf{Experience:} Python, Databricks, Deltalake, Jenkins, Recommendations, Real-time Model Inference, Batch Model Inference, AWS, Embedding based retrieval }
\end{job}


\begin{job}
{Aug 2020-}{Apr 2021}
{Dataswift, Remote Canada}
{https://dataswift.io/}
{Senior Backend Engineer}%
{Early stage startup, I joined the engineering team during an era of rapid growth and was pivotal in productionizing the system (micro-service data processing) and growing the team. Technical responsibilities included; designing, developing, refactoring of API and backend systems. Defining standards, testing, setting up development system and technical road maps. Non technical included  mentoring, creating the software development process and hiring.  \\
\rule{0mm}{5mm}\textbf{Experience:} Scala, Testing, Functional Programming, Cats, AWS, Dev Ops, Docker, SQL, Postgres}
\end{job}

\begin{job}
{Oct 2017-}{July 2020}
{Contracting to Avalanche Canada, Revelstoke British Columbia Canada}
{http://www.Avalanche.ca}
{Project Manager / Senior Backend Engineer}%
{Developed workflow and data aggregation/visualisation tools for Avalanche Forecasting. In conjunction with internal staff worked from initial brainstorming through requirements gathering, development, testing and deployment. My role as  project manager had me working directly with users, planning and coordinating contractors (for front end). My secondary role was as the backend developer where I developed data API's, managed infra and CI/CD.\\
\rule{0mm}{5mm}\textbf{Experience:} Scala, Functional Programming, Cats, AWS, Dev Ops, Jenkins, Docker, SQL, Postgres}
\end{job}

\begin{job}
{Sep 2016 -}{Oct 2017}
{Amazon, Vancouver British Columbia Canada}
{http://www.Amazon.ca}
{Software Development Engineer}%
{Technical Lead developing a data platform service for Machine Learning, Data Analysis and Investigation teams in Anti Money Laundering (Seller Compliance / Suspicious Activity Monitoring). \\
\rule{0mm}{5mm}\textbf{Experience:} Java, Scala, AWS, Git, SCRUM, Hiring, Documentation, Dev ops}
\end{job}


\begin{job}
{Aug 2015 -}{Aug 2016}
{Amazon, Toronto Ontario Canada}
{http://www.Amazon.ca}
{Software Development Engineer}%
{Developed a service to streamline, extraction, processing, access and discovery of big data for scientists and business analysts. The platform is based on-top of Spark and Hadoop and utilises AWS technologies to add discovery of datasets using metadata \\
\rule{0mm}{5mm}\textbf{Experience:} Big Data, Java, Scala, Python, Hadoop, Spark, AWS, Git, SCRUM, Hiring, Dev ops}
\end{job}

\begin{job}
{Mar 2014 -}{Aug 2015}
{Avalanche Canada, Revelstoke British Columbia Canada}
{http://www.avalanche.ca}
{Senior Software Developer}%
{When the CAA (Canadian Avalanche Association) and CAC (Canadian Avalanche Centre) boards decided that they wanted individual organisations we dissolved the existing IT team and split staff between the two. I went with the CAC which was re-branded Avalanche Canada. Part of this re-brand was to develop a new website from the ground up with an extremely limited budget. I worked closely with management to determine the technical direction of the re-branded organisation and was the lead developer of the new website and phone application working with several contractors and contributors to develop a new open source platform and website for Avalanche Information in Canada. \\
\rule{0mm}{5mm}\textbf{Experience:} Management, Budgeting, Open Source, Javascript, Node.js, GitHub, Angular.js, REST, AWS, Hiring }
\end{job}

\begin{job}
{Jun 2012 -}{Mar 2014}
{Canadian Avalanche Association, Revelstoke British Columbia Canada}
{http://www.avalanche.ca}
{Senior Software Developer}%
{Led a team responsible for the maintenance and development of all IT systems for both the Canadian Avalanche Centre and Canadian Avalanche Association. This included Website, phone application, infrastructure, and database as well as managing other IT staff (3 direct reports)\\
\rule{0mm}{5mm}\textbf{Experience:} Javascript, AngularJs, Heroku, .Net} 
\end{job}

\begin{job}
{Jun 2007 -}{Jun 2012}
{CEA Technologies, Fyshwick Canberra Australia}
{http://www.cea.com.au}
{Embedded Software Engineer}%
{Responsible for the design, development, testing and documentation of embedded software to perform signal processing and control of radar systems. Software was run on a distributed processing system using of the shelf boards and a Real Time Operating System. For the CEAMOUNT project I was the team leader for the software component.\\
\rule{0mm}{5mm}\textbf{Experience:} Radar Systems, C++, Assembly, Real Time Operating Systems, Embedded Development, Signal Processing, Scheduling, Concurrency, Distributed Processing, Qt, Hiring} 
\end{job}

% Education section
\section*{Education}

\begin{education}
{2003-2006}
{University of Canberra, Australia} 
{http://www.canberra.edu.au/} 
{First class Hons BE in Software Engineering}%
\textit{Honours Thesis - Real-time decision making for an autonomous vehicles, simulated
on PS2 hardware.}\\
\rule{0mm}{5mm}\textbf{Units:} {AI, Biometric authentication, Project management, Software development, Database systems, Math, Processor design, Digital circuits, Computer hardware, Machine learning, Games Programming, Operating systems.} 
\end{education}

% Interests section
\section*{Interests}

\begin{tabbing}
\hspace{5mm} \= \kill
\rule{0mm}{4mm}\sqbullet \> \textbf{Snowboarding}\\
\rule{0mm}{4mm}\sqbullet \> \textbf{Rock Climbing} \\
\rule{0mm}{4mm}\sqbullet \> \textbf{Mountain Biking} \\
\rule{0mm}{4mm}\sqbullet \> \textbf{Linux} \\
\end{tabbing}

\end{document}
